---
title: "vast_kallisto_majiq_sp-stringtie"
output: html_document
---

most of this is a re-hashing of majiq/dAS_analysis/kallisto_vast_majiq.Rmd, with the notable difference of stringtie data being included. The graphs will also be reformatted in decreasing order of soil water content, as that seems to be more intuitive to other people. 

```{r}
library(tidyverse)
library(scales)
library(ggVennDiagram)
```

vast-tools:
```{r}
vast_k20dk20w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K20d-K20w_68events/K20d-K20w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K20dK20w"))

vast_k20dl20d <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K20d-L20d_327events/K20d-L20d_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K20dL20d"))

vast_k20wl20w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K20w-L20w_196events/K20w-L20w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K20wL20w"))

vast_k40dk40w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K40d-K40w_23events/K40d-K40w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K40dK40w"))

vast_k40dl40d <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K40d-L40d_168events/K40d-L40d_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K40dL40d"))

vast_k40wl40w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K40w-L40w_69events/K40w-L40w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K40wL40w"))

vast_k60dk60w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K60d-K60w_6events/K60d-K60w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K60dK60w"))

vast_k60dl60d <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K60d-L60d_94events/K60d-L60d_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K60dL60d"))

vast_k60wl60w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/K60w-L60w_58events/K60w-L60w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("K60wL60w"))

vast_l20dl20w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/L20d-L20w_706events/L20d-L20w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("L20dL20w"))

vast_l40dl40w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/L40d-L40w_27events/L40d-L40w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("L40dL40w"))

vast_l60dl60w <- read_delim("../../vasttools/all_data/dPSI25_no_merging_all_reps/L60d-L60w_5events/L60d-L60w_compare_ouput_complete.tab", col_names = T, delim = "\t") %>% 
  select(GeneID) %>% 
  mutate(prog = c("vast-tools"), comp = c("L60dL60w"))
```

kallisto:
```{r}
kallisto_k20dk20w <- read_delim("../../kallisto/dAS_analysis/dAS_K20dK20w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K20dK20w"))

kallisto_k40dk40w <- read_delim("../../kallisto/dAS_analysis/dAS_K40dK40w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K40dK40w"))

kallisto_k60dk60w <- read_delim("../../kallisto/dAS_analysis/dAS_K60dK60w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K60dK60w"))

kallisto_l20dl20w <- read_delim("../../kallisto/dAS_analysis/dAS_L20dL20w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("L20dL20w"))

kallisto_l40dl40w <- read_delim("../../kallisto/dAS_analysis/dAS_L40dL40w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("L40dL40w"))

kallisto_l60dl60w <- read_delim("../../kallisto/dAS_analysis/dAS_L60dL60w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("L60dL60w"))

kallisto_k20dl20d <- read_delim("../../kallisto/dAS_analysis/dAS_K20dL20d_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K20dL20d"))

kallisto_k40dl40d <- read_delim("../../kallisto/dAS_analysis/dAS_K40dL40d_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K40dL40d"))

kallisto_k60dl60d <- read_delim("../../kallisto/dAS_analysis/dAS_K60dL60d_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K60dL60d"))

kallisto_k20wl20w <- read_delim("../../kallisto/dAS_analysis/dAS_K20wL20w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K20wL20w"))

kallisto_k40wl40w <- read_delim("../../kallisto/dAS_analysis/dAS_K40wL40w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K40wL40w"))

kallisto_k60wl60w <- read_delim("../../kallisto/dAS_analysis/dAS_K60wL60w_kallisto.txt", col_names = T, delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("kallisto"), comp = c("K60wL60w"))
```

majiq:
```{r}
majiq_k20dk20w <- read_delim("../../majiq/dAS_analysis/filter25/K20dK20w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K20dK20w"))

majiq_k40dk40w <- read_delim("../../majiq/dAS_analysis/filter25/K40dK40w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K40dK40w"))

majiq_k60dk60w <- read_delim("../../majiq/dAS_analysis/filter25/K60dK60w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K60dK60w"))

majiq_l20dl20w <- read_delim("../../majiq/dAS_analysis/filter25/L20dL20w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("L20dL20w"))

majiq_l40dl40w <- read_delim("../../majiq/dAS_analysis/filter25/L40dL40w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("L40dL40w"))

majiq_l60dl60w <- read_delim("../../majiq/dAS_analysis/filter25/L60dL60w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("L60dL60w"))

majiq_k20dl20d <- read_delim("../../majiq/dAS_analysis/filter25/K20dL20d.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K20dL20d"))

majiq_k40dl40d <- read_delim("../../majiq/dAS_analysis/filter25/K40dL40d.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K40dL40d"))

majiq_k60dl60d <- read_delim("../../majiq/dAS_analysis/filter25/K60dL60d.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K60dL60d"))

majiq_k20wl20w <- read_delim("../../majiq/dAS_analysis/filter25/K20wL20w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K20wL20w"))

majiq_k40wl40w <- read_delim("../../majiq/dAS_analysis/filter25/K40wL40w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K40wL40w"))

majiq_k60wl60w <- read_delim("../../majiq/dAS_analysis/filter25/K60wL60w.tsv", delim = "\t") %>% 
  select(`Gene ID`) %>% 
  mutate(prog = c("majiq"), comp = c("K60wL60w"))
```

stringtie:
```{r}
stringtie_k20dk20w <- read_delim("dAS_K20dK20w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K20dK20w"))

stringtie_k40dk40w <- read_delim("dAS_K40dK40w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K40dK40w"))

stringtie_k60dk60w <- read_delim("dAS_K60dK60w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K60dK60w"))

stringtie_l20dl20w <- read_delim("dAS_L20dL20w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("L20dL20w"))

stringtie_l40dl40w <- read_delim("dAS_L40dL40w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("L40dL40w"))

stringtie_l60dl60w <- read_delim("dAS_L60dL60w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("L60dL60w"))

stringtie_k20dl20d <- read_delim("dAS_K20dL20d_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K20dL20d"))

stringtie_k40dl40d <- read_delim("dAS_K40dL40d_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K40dL40d"))

stringtie_k60dl60d <- read_delim("dAS_K60dL60d_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K60dL60d"))

stringtie_k20wl20w <- read_delim("dAS_K20wL20w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K20wL20w"))

stringtie_k40wl40w <- read_delim("dAS_K40wL40w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K40wL40w"))

stringtie_k60wl60w <- read_delim("dAS_K60wL60w_stringtie.txt", delim = "\t") %>% 
  select(gene_id) %>% 
  mutate(prog = c("stringtie"), comp = c("K60wL60w"))
```

ok, so let's do the graphs of AS genes by comparison group for each program. Gonna switch the order to decreasing soil water content, cause the other way around seems to confuse people.

create a list of unique genes in each comparison
```{r}
K20dK20w <- unique(c(vast_k20dk20w$GeneID, kallisto_k20dk20w$gene_id, majiq_k20dk20w$`Gene ID`, stringtie_k20dk20w$gene_id))
K40dK40w <- unique(c(vast_k40dk40w$GeneID, kallisto_k40dk40w$gene_id, majiq_k40dk40w$`Gene ID`, stringtie_k40dk40w$gene_id))
K60dK60w <- unique(c(vast_k60dk60w$GeneID, kallisto_k60dk60w$gene_id, majiq_k60dk60w$`Gene ID`, stringtie_k60dk60w$gene_id))

L20dL20w <- unique(c(vast_l20dl20w$GeneID, kallisto_l20dl20w$gene_id, majiq_l20dl20w$`Gene ID`, stringtie_l20dl20w$gene_id))
L40dL40w <- unique(c(vast_l40dl40w$GeneID, kallisto_l40dl40w$gene_id, majiq_l40dl40w$`Gene ID`, stringtie_l40dl40w$gene_id))
L60dL60w <- unique(c(vast_l60dl60w$GeneID, kallisto_l60dl60w$gene_id, majiq_l60dl60w$`Gene ID`, stringtie_l60dl60w$gene_id))

K20dL20d <- unique(c(vast_k20dl20d$GeneID, kallisto_k20dl20d$gene_id, majiq_k20dl20d$`Gene ID`, stringtie_k20dl20d$gene_id))
K40dL40d <- unique(c(vast_k40dl40d$GeneID, kallisto_k40dl40d$gene_id, majiq_k40dl40d$`Gene ID`, stringtie_k40dl40d$gene_id))
K60dL60d <- unique(c(vast_k60dl60d$GeneID, kallisto_k60dl60d$gene_id, majiq_k60dl60d$`Gene ID`, stringtie_k60dl60d$gene_id))

K20wL20w <- unique(c(vast_k20wl20w$GeneID, kallisto_k20wl20w$gene_id, majiq_k20wl20w$`Gene ID`, stringtie_k20wl20w$gene_id))
K40wL40w <- unique(c(vast_k40wl40w$GeneID, kallisto_k40wl40w$gene_id, majiq_k40wl40w$`Gene ID`, stringtie_k40wl40w$gene_id))
K60wL60w <- unique(c(vast_k60wl60w$GeneID, kallisto_k60wl60w$gene_id, majiq_k60wl60w$`Gene ID`, stringtie_k60wl60w$gene_id))
```

assign each gene a column for the program(s) to which it belongs and step 4: join program columns together
```{r}
#this may objectively be some of the ugliest code I've ever written... find a way to clean this up!
#any and all attempts at writing a function for this have been met with failure
#so it's staying ugly for now grrrr

K20dK20w <- as.data.frame(K20dK20w)
colnames(K20dK20w) <- "gene"
K20dK20w <- K20dK20w %>% mutate(prog1 = if_else(gene %in% vast_k20dk20w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k20dk20w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k20dk20w$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_k20dk20w$gene_id, "stringtie", "NA"))  
K20dK20w[K20dK20w == "NA"] = NA
K20dK20w <- unite(K20dK20w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K20dK20w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

K40dK40w <- as.data.frame(K40dK40w)
colnames(K40dK40w) <- "gene"
K40dK40w <- K40dK40w %>% mutate(prog1 = if_else(gene %in% vast_k40dk40w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k40dk40w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k40dk40w$`Gene ID`, "majiq", "NA"),prog4 = if_else(gene %in% stringtie_k40dk40w$gene_id, "stringtie", "NA")) 
K40dK40w[K40dK40w == "NA"] = NA
K40dK40w <- unite(K40dK40w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K40dK40w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

K60dK60w <- as.data.frame(K60dK60w)
colnames(K60dK60w) <- "gene"
K60dK60w <- K60dK60w %>% mutate(prog1 = if_else(gene %in% vast_k60dk60w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k60dk60w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k60dk60w$`Gene ID`, "majiq", "NA"),prog4 = if_else(gene %in% stringtie_k60dk60w$gene_id, "stringtie", "NA")) 
K60dK60w[K60dK60w == "NA"] = NA
K60dK60w <- unite(K60dK60w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K60dK60w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

L20dL20w <- as.data.frame(L20dL20w)
colnames(L20dL20w) <- "gene"
L20dL20w <- L20dL20w %>% mutate(prog1 = if_else(gene %in% vast_l20dl20w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_l20dl20w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_l20dl20w$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_l20dl20w$gene_id, "stringtie", "NA")) 
L20dL20w[L20dL20w == "NA"] = NA
L20dL20w <- unite(L20dL20w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("L20dL20w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

L40dL40w <- as.data.frame(L40dL40w)
colnames(L40dL40w) <- "gene"
L40dL40w <- L40dL40w %>% mutate(prog1 = if_else(gene %in% vast_l40dl40w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_l40dl40w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_l40dl40w$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_l40dl40w$gene_id, "stringtie", "NA")) 
L40dL40w[L40dL40w == "NA"] = NA
L40dL40w <- unite(L40dL40w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("L40dL40w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

L60dL60w <- as.data.frame(L60dL60w)
colnames(L60dL60w) <- "gene"
L60dL60w <- L60dL60w %>% mutate(prog1 = if_else(gene %in% vast_l60dl60w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_l60dl60w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_l60dl60w$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_l60dl60w$gene_id, "stringtie", "NA")) 
L60dL60w[L60dL60w == "NA"] = NA
L60dL60w <- unite(L60dL60w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("L60dL60w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

K20dL20d <- as.data.frame(K20dL20d)
colnames(K20dL20d) <- "gene"
K20dL20d <- K20dL20d %>% mutate(prog1 = if_else(gene %in% vast_k20dl20d$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k20dl20d$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k20dl20d$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_k20dl20d$gene_id, "stringtie", "NA")) 
K20dL20d[K20dL20d == "NA"] = NA
K20dL20d <- unite(K20dL20d, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K20dL20d"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

K40dL40d <- as.data.frame(K40dL40d)
colnames(K40dL40d) <- "gene"
K40dL40d <- K40dL40d %>% mutate(prog1 = if_else(gene %in% vast_k40dl40d$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k40dl40d$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k40dl40d$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_k40dl40d$gene_id, "stringtie", "NA")) 
K40dL40d[K40dL40d == "NA"] = NA
K40dL40d <- unite(K40dL40d, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K40dL40d"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

K60dL60d <- as.data.frame(K60dL60d)
colnames(K60dL60d) <- "gene"
K60dL60d <- K60dL60d %>% mutate(prog1 = if_else(gene %in% vast_k60dl60d$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k60dl60d$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k60dl60d$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_k60dl60d$gene_id, "stringtie", "NA")) 
K60dL60d[K60dL60d == "NA"] = NA
K60dL60d <- unite(K60dL60d, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K60dL60d"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

K20wL20w <- as.data.frame(K20wL20w)
colnames(K20wL20w) <- "gene"
K20wL20w <- K20wL20w %>% mutate(prog1 = if_else(gene %in% vast_k20wl20w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k20wl20w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k20wl20w$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_k20wl20w$gene_id, "stringtie", "NA")) 
K20wL20w[K20wL20w == "NA"] = NA
K20wL20w <- unite(K20wL20w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K20wL20w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

K40wL40w <- as.data.frame(K40wL40w)
colnames(K40wL40w) <- "gene"
K40wL40w <- K40wL40w %>% mutate(prog1 = if_else(gene %in% vast_k40wl40w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k40wl40w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k40wl40w$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_k40wl40w$gene_id, "stringtie", "NA")) 
K40wL40w[K40wL40w == "NA"] = NA
K40wL40w <- unite(K40wL40w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K40wL40w"))%>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)

K60wL60w <- as.data.frame(K60wL60w)
colnames(K60wL60w) <- "gene"
K60wL60w <- K60wL60w %>% mutate(prog1 = if_else(gene %in% vast_k60wl60w$GeneID, "vast-tools", "NA"), prog2 = if_else(gene %in% kallisto_k60wl60w$gene_id, "kallisto", "NA"), prog3 = if_else(gene %in% majiq_k60wl60w$`Gene ID`, "majiq", "NA"), prog4 = if_else(gene %in% stringtie_k60wl60w$gene_id, "stringtie", "NA")) 
K60wL60w[K60wL60w == "NA"] = NA
K60wL60w <- unite(K60wL60w, prog, c(prog1, prog2, prog3, prog4), na.rm = T, remove = F) %>% 
  mutate(comp = c("K60wL60w")) %>% 
  unite(prog_vm, c(prog1, prog3), na.rm = T, remove = F) %>% 
  unite(prog_vk, c (prog1, prog2), na.rm = T, remove = F) %>% 
  unite(prog_vs, c (prog1, prog4), na.rm = T, remove = F) %>%
  unite(prog_km, c (prog3, prog2), na.rm = T, remove = F) %>% 
  unite(prog_ks, c (prog4, prog2), na.rm = T, remove = F) %>%
  unite(prog_ms, c (prog4, prog3), na.rm = T, remove = F)
```

plot by program:
```{r}
show_col(hue_pal()(15))

order <- c("K60dK60w", "K40dK40w", "K20dK20w", "L60dL60w", "L40dL40w", "L20dL20w", "K60dL60d", "K40dL40d", "K20dL20d", "K60wL60w", "K40wL40w", "K20wL20w")

kallisto_all <- rbind(kallisto_k20dk20w,  kallisto_k40dk40w, kallisto_k60dk60w, kallisto_l20dl20w, kallisto_l40dl40w, kallisto_l60dl60w, kallisto_k20dl20d,kallisto_k40dl40d,kallisto_k60dl60d, kallisto_k20wl20w, kallisto_k40wl40w, kallisto_k60wl60w)

kallisto_all <- kallisto_all %>% 
  group_by(comp) %>% 
  summarize(count = n())%>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(kallisto_all, aes(x = fct_inorder(comp), y = count))+
  geom_bar(stat = "identity", fill = "#F8766D")
dev.off()
```

```{r}
vast_all <- rbind(vast_k20dk20w, vast_k20dl20d, vast_k20wl20w, vast_k40dk40w, vast_k40dl40d, vast_k40wl40w, vast_k60dk60w, vast_k60dl60d, vast_k60wl60w, vast_l20dl20w, vast_l40dl40w, vast_l60dl60w)

vast_all <- vast_all %>% 
  group_by(comp) %>% 
  summarize(count = n()) %>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(vast_all, aes(x = fct_inorder(comp), y = count))+
  geom_bar(stat = "identity", fill = "#B983FF")
dev.off()
```

```{r}
majiq_all <- rbind(majiq_k20dk20w, majiq_k20dl20d, majiq_k20wl20w, majiq_k40dk40w, majiq_k40dl40d, majiq_k40wl40w, majiq_k60dk60w, majiq_k60dl60d, majiq_k60wl60w, majiq_l20dl20w, majiq_l40dl40w, majiq_l60dl60w)

majiq_all <- majiq_all %>% 
  group_by(comp) %>% 
  summarize(count = n()) %>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(majiq_all, aes(x = fct_inorder(comp), y = count))+
  geom_bar(stat = "identity", fill = "#6BB100")
dev.off()
```

```{r}
stringtie_all <- rbind(stringtie_k20dk20w, stringtie_k20dl20d, stringtie_k20wl20w, stringtie_k40dk40w, stringtie_k40dl40d, stringtie_k40wl40w, stringtie_k60dk60w, stringtie_k60dl60d, stringtie_k60wl60w, stringtie_l20dl20w, stringtie_l40dl40w,stringtie_l60dl60w)

stringtie_all <- stringtie_all %>% 
  group_by(comp) %>% 
  summarize(count = n()) %>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(stringtie_all, aes(x = fct_inorder(comp), y = count))+
  geom_bar(stat = "identity", fill = "#00BF7D")
dev.off()
```


rbind, group_by, summarize and plot!
```{r}
all <- rbind(K20dK20w, K40dK40w, K60dK60w, L20dL20w, L40dL40w, L60dL60w, K20dL20d, K40dL40d, K60dL60d, K20wL20w, K40wL40w, K60wL60w)
all[all == ""] = NA
to_plot <- all %>% group_by(prog, comp, prog_vm, prog_vk, prog_vs, prog_km, prog_ks, prog_ms) %>% 
  summarize(count = n()) %>% 
  mutate(comp = factor(comp, levels = order)) %>% 
  arrange(comp)
```

```{r}
png("test.png", units="in", width=15, height=8, res=300)
ggplot(to_plot, aes(x = fct_inorder(comp), y = count, fill = prog))+
  geom_bar(stat = "identity")
dev.off()
```

as expected, this graph is super duper hard to understand. there's too many programs and comparisons in the same graph, so while it's efficient, it's complicated. We can either show less comps, or less programs. Something to pick other people's brains about...

how bout 2 programs at a time?
vast-majiq:
```{r}
to_plot_vm <- to_plot %>% filter(!is.na(prog_vm))
colours <- c("#6BB100", "#B983FF", "#E58700")
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(to_plot_vm, aes(x = comp, y = count, fill = prog_vm))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = colours)
dev.off()
```

vast-kallisto:
```{r}
to_plot_vk <- to_plot %>% filter(!is.na(prog_vk))
colours <- c("#F8766D", "#B983FF", "#E58700")
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(to_plot_vk, aes(x = comp, y = count, fill = prog_vk))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = colours)
dev.off()
```

vast-stringtie
```{r}
to_plot_vs <- to_plot %>% filter(!is.na(prog_vs))
colours <- c("#00BF7D", "#B983FF", "#E58700")
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(to_plot_vs, aes(x = comp, y = count, fill = prog_vs))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = colours)
dev.off()
```

kallisto-majiq
```{r}
to_plot_km <- to_plot %>% filter(!is.na(prog_km))
colours <- c("#F8766D", "#6BB100", "#E58700")
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(to_plot_km, aes(x = comp, y = count, fill = prog_km))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = colours)
dev.off()
```

kallisto-stringtie
```{r}
to_plot_ks <- to_plot %>% filter(!is.na(prog_ks))
colours <- c("#F8766D", "#00BF7D", "#E58700")
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(to_plot_ks, aes(x = comp, y = count, fill = prog_ks))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = colours)
dev.off()
```

majiq-stringtie
```{r}
to_plot_ms <- to_plot %>% filter(!is.na(prog_ms))
colours <- c("#6BB100", "#00BF7D", "#E58700")
```

```{r}
png("test.png", units="in", width=15, height=3, res=300)
ggplot(to_plot_ms, aes(x = comp, y = count, fill = prog_ms))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = colours)
dev.off()
```

plotting a venn diagram requires a list of named vectors:
K20dK20w
```{r}
k20dk20w_venn <- list(vast_k20dk20w$GeneID, kallisto_k20dk20w$gene_id, majiq_k20dk20w$`Gene ID`, stringtie_k20dk20w$gene_id)

l20dl20w_venn <- list(vast_l20dl20w$GeneID, kallisto_l20dl20w$gene_id, majiq_l20dl20w$`Gene ID`, stringtie_l20dl20w$gene_id)
```

```{r}
png("test.png", units="in", width=20, height=15, res=300)
ggVennDiagram(k20dk20w_venn,
              label_color = "black",
              label_alpha = 0,
              label_size = 10,
              category.names = c("vast-tools", "kallisto", "majiq", "stringtie"),
              set_size = 10,
              edge_size = 2)+
  scale_fill_gradient(high = "blue", low = "white")+
  theme(legend.key.size = unit(2, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size = 15))
dev.off()
```

```{r}
png("test.png", units="in", width=20, height=15, res=300)
ggVennDiagram(l20dl20w_venn,
              label_color = "black",
              label_alpha = 0,
              label_size = 10,
              category.names = c("vast-tools", "kallisto", "majiq", "stringtie"),
              set_size = 10,
              edge_size = 2)+
  scale_fill_gradient(high = "blue", low = "white")+
  theme(legend.key.size = unit(2, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size = 15))
dev.off()
```

mega venn diagram! need a list of gene-comp pairs for each program
```{r}
kallisto_long <- rbind(kallisto_k20dk20w,  kallisto_k40dk40w, kallisto_k60dk60w, kallisto_l20dl20w, kallisto_l40dl40w, kallisto_l60dl60w, kallisto_k20dl20d,kallisto_k40dl40d,kallisto_k60dl60d, kallisto_k20wl20w, kallisto_k40wl40w, kallisto_k60wl60w)
kallisto_long$gene_comp <- str_c(kallisto_long$gene_id, kallisto_long$comp)

stringtie_long <- rbind(stringtie_k20dk20w, stringtie_k20dl20d, stringtie_k20wl20w, stringtie_k40dk40w, stringtie_k40dl40d, stringtie_k40wl40w, stringtie_k60dk60w, stringtie_k60dl60d, stringtie_k60wl60w, stringtie_l20dl20w, stringtie_l40dl40w,stringtie_l60dl60w)
stringtie_long$gene_comp <- str_c(stringtie_long$gene_id, stringtie_long$comp)

majiq_long <- rbind(majiq_k20dk20w, majiq_k20dl20d, majiq_k20wl20w, majiq_k40dk40w, majiq_k40dl40d, majiq_k40wl40w, majiq_k60dk60w, majiq_k60dl60d, majiq_k60wl60w, majiq_l20dl20w, majiq_l40dl40w, majiq_l60dl60w)
majiq_long$gene_comp <- str_c(majiq_long$`Gene ID`, majiq_long$comp)

vast_long <- rbind(vast_k20dk20w, vast_k20dl20d, vast_k20wl20w, vast_k40dk40w, vast_k40dl40d, vast_k40wl40w, vast_k60dk60w, vast_k60dl60d, vast_k60wl60w, vast_l20dl20w, vast_l40dl40w, vast_l60dl60w)
vast_long$gene_comp=str_c(vast_long$GeneID, vast_long$comp)

mega_venn <- list(vast_long$gene_comp, kallisto_long$gene_comp, majiq_long$gene_comp, stringtie_long$gene_comp)
```

```{r}
png("test.png", units="in", width=20, height=15, res=300)
ggVennDiagram(mega_venn,
              label_color = "black",
              label_alpha = 0,
              label_size = 9,
              category.names = c("VAST-TOOLS", "kallisto", "MAJIQ", "StringTie"),
              set_size = 9,
              edge_size = 2)+
  scale_fill_gradient(high = "blue", low = "white")+
  theme(legend.key.size = unit(2, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size = 15))
dev.off()
```

